### 2016-07-06 store-consistency.tex
edits

}
\hspace*{0.1in}
\subcaptionbox {
  Subset model
  \label{fig:ec-ours}
}{
  \includegraphics[scale=0.35]{Figures/ec-ours}
} \caption{\small In the replica model, operation $\op$ generates effect
$\eta$ at replica $R_1$, which is then merged to $R_2$. If the
\emph{store is {\sc cc}}, then $R_2$'s state at merge event is same or
larger than $R_1$'s state at generation event (the difference is
highlighted). In our subset model, $\op$ witnesses $S_1 \subseteq
\E.\A$ and generates $\eta$, which is immediately added to $\E.\A$. A
later operation may witness $S_2 \subseteq \E.\A$, and if the
\emph{operation is} {\sc cc} and $\eta \in S_2$, then it also
witnesses $S_1$ (i.e., $S_1 \subseteq S_2$). } 
% Moreover, Like $R_2 - R_1$, if all effects in $S_2 - S_1$ are
% concurrent with $\eta$, i.e., $\not\exists\eta'.~\eta' \in S_2 - S_1
% \conj % visZ(\eta,\eta')$, then any pre-condition $P$ that is valid
% when $\op$ executed is also valid when $\eta$ is witnessed because
% of the stability condition.
\label{fig:ec-theirs-vs-ours}
\end{figure}

@@

Decorated parts of \C{Wd1} relevant to the discussion are shown in
Fig.~\ref{fig:wd1-decorated}.  \C{Wd2} is similar and not
shown\footnote{The supplementary material shows the fully decorated program.}.
Temporary name \C{v3} has been introduced to capture the result of the
RHS expression \C{C-a1}.  Assertions implicitly refer to the current
execution ($\E$), just as Hoare triples implicitly refer to the
current state.  The context for propositions is also the implicit,
i.e., we write $\psi$ instead of $\underE{\psi}$. The proposition \C{k
$\ge$ a1+a2} remains an invariant, hence elided. The pre-condition
$P_1$ of \C{Wd1} accounts for the possibility of \C{Wd2} committing
before \C{Wd1}, writing \C{k-a2} to \C{B}. Since neither \C{Wd1} nor
\C{Wd2} are committed at the beginning, the pre-condition $P$ of the
program is extended with $\neg\committed(\C{Wd1}) \wedge
\neg\committed(\C{Wd2})$, from which $P_1$ follows. The post-condition
$Q_1$ of \C{Wd1} asserts different values for \C{B} depending on
whether or not \C{Wd2} has already committed.  It also asserts that
\C{Wd1} has committed. The post-condition $Q_2$ of \C{Wd2} (not shown)
is similar, but with the roles of \C{Wd1} and \C{Wd2} exchanged. The
post-condition $Q$ follows from $Q_1 \wedge Q_2$, hence valid. It
remains to show that \C{Wd1} satisfies its specification (\C{Wd2} must
also satisfy its spec, but the proof is similar).

>>>>

}
\hspace*{0.1in}
\subcaptionbox {
  Subset model
  \label{fig:ec-ours}
}{
  \includegraphics[scale=0.35]{Figures/ec-ours}
} \caption{\small In the replica model, operation $\op$ generates effect
$\eta$ at replica $R_1$, which is then merged to $R_2$. If the
\emph{store is {\sc cc}}, then $R_2$'s state at the merge event is same or
larger than $R_1$'s state at the generation event (the difference is
highlighted). In our subset model, $\op$ witnesses $S_1 \subseteq
\E.\A$ and generates $\eta$, which is immediately added to $\E.\A$. A
later operation may witness $S_2 \subseteq \E.\A$, and if the
\emph{operation is} {\sc cc} and $\eta \in S_2$, then it also
witnesses $S_1$ (i.e., $S_1 \subseteq S_2$). } 
% Moreover, Like $R_2 - R_1$, if all effects in $S_2 - S_1$ are
% concurrent with $\eta$, i.e., $\not\exists\eta'.~\eta' \in S_2 - S_1
% \conj % visZ(\eta,\eta')$, then any pre-condition $P$ that is valid
% when $\op$ executed is also valid when $\eta$ is witnessed because
% of the stability condition.
\label{fig:ec-theirs-vs-ours}
\end{figure}

@@

Decorated parts of \C{Wd1} relevant to the discussion are shown in
Fig.~\ref{fig:wd1-decorated}.  \C{Wd2} is similar and not
shown.\footnote{The supplementary material shows the fully decorated program.}
Temporary name \C{v3} has been introduced to capture the result of the
RHS expression \C{C-a1}.  Assertions implicitly refer to the current
execution ($\E$), just as Hoare triples implicitly refer to the
current state.  The context for propositions is also the implicit,
i.e., we write $\psi$ instead of $\underE{\psi}$. The proposition \C{k
$\ge$ a1+a2} remains an invariant, hence elided. The pre-condition
$P_1$ of \C{Wd1} accounts for the possibility of \C{Wd2} committing
before \C{Wd1}, writing \C{k-a2} to \C{B}. Since neither \C{Wd1} nor
\C{Wd2} are committed at the beginning, the pre-condition $P$ of the
program is extended with $\neg\committed(\C{Wd1}) \wedge
\neg\committed(\C{Wd2})$, from which $P_1$ follows. The post-condition
$Q_1$ of \C{Wd1} asserts different values for \C{B} depending on
whether or not \C{Wd2} has already committed.  It also asserts that
\C{Wd1} has committed. The post-condition $Q_2$ of \C{Wd2} (not shown)
is similar, but with the roles of \C{Wd1} and \C{Wd2} exchanged. The
post-condition $Q$ follows from $Q_1 \wedge Q_2$, hence valid. It
remains to show that \C{Wd1} satisfies its specification (\C{Wd2} must
also satisfy its spec, but the proof is similar).
